SpARC: Sparse Redundant Calibration

### 2016-09-21 paper.tex
paper.tex

>>>>

\section{Visibilities}
The observed visibility $d_{pq}$ measured by the baseline formed by antenna $p$ and $q$ is described by
\begin{equation}
d_{pq} = g_{p}\conj{g}_{q}y_{pq} + n_{pq},
\end{equation}
where $g_{p}$ and $g_{q}$ are the direction independent gains respectively associated with antenna $p$ and $q$, $y_{pq}$ denotes the true visibility that baseline $pq$ measured
and $n_{pq}$ is the thermal noise. Conjugation is denoted by $\conj{(*)}$. During an actual observation the true value of $g_p$, $g_q$ and $y_{pq}$ are unknown and are the quantities which have 
to be estimated.

The thermal noise has zero-mean and is normally distrubuted with standard deviation  
\begin{equation}

\end{equation}

and $n_{pq}$ 
zero-mean gaussian noise representing thermal noise.
